Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-06 edubots_surveys.Rnw
fix errors and grammar - introduction par2

\textcolor{blue}{In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
In addition to their main use, some of these tools offer the possibility of interact with \textit{chatbots} (or just bots), even supporting synchronous conversation between the different
parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).}

>>>>

\textcolor{blue}{Messaging applications such as WhatsApp or Telegram are becoming very popular in teaching scenarios mainly at secondary and higher education.
In addition to their main use, some of these tools offer the possibility to interact with \textit{chatbots} (or just bots), even supporting synchronous conversations between the different
parties \cite{differ.chat}. It is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Programming Interface).}
